Plots

### 2025-08-13 src/plots.Rmd
Finished initial draft of v2

# Plot adult perf for pccc by cod
fig_pccc_cod_adult <- plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
    text_mid_vjust = 2,
    text_scale = 1
)

@@

# Plot neo perf for pccc by cod
fig_pccc_cod_neo <- plot_perf(
    df_long %>% filter(age == "neo"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Neonatal, <28 Days (n=", n_neo, ")"),
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    text_mid_vjust = 3,
    text_scale = 1.25
)

@@

# Plot perf trend over age ranges
fig_pccc_age <- plot_perf_trend(
    df_long %>%
        mutate(
            age_range = str_replace(age_range, " ", "\n") %>%
                factor(., levels = age_levels)
        ),
    title = "Partial Chance Corrected Concordance (PCCC)",
    text_scale = 0.9
)

>>>>

# Plot adult perf for pccc by cod
fig_pccc_cod_adult <- plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
    text_mid_vjust = 2.5,
    text_scale = 1
)

@@

# Plot neo perf for pccc by cod
fig_pccc_cod_neo <- plot_perf(
    df_long %>% filter(age == "neo"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Neonatal, <28 Days (n=", n_neo, ")"),
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    text_mid_vjust = 3.5,
    text_scale = 1.25
)

@@

# Plot perf trend over age ranges
fig_pccc_age <- plot_perf_trend(
    df_long %>%
        mutate(
            age_range = str_replace(age_range, " ", "\n") %>%
                factor(., levels = age_levels)
        ),
    y_title = "Partial Chance Corrected Concordance (PCCC)",
    text_scale = 0.9
)
